CFTP Convergence

### 2025-02-11 extensive_tests/CFTP_convergence/draft-test_CFTP_convergence.Rmd
began breaking lines
Updating changes in draft CFTP convergence

q---
title: "CFTP Convergence"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Test for CFTP Convergence}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

>>>>

---
title: "CFTP Convergence"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Test for CFTP Convergence}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

# TO ADD

- Add references

- Simplify sentences

- Step in the Workflow and then mention Snakemake and conda as an additional option.

- Instead of whan using nohup, if using nohup
